---
title: "TP2"
author: "Erica Bucchieri & Stephen Durbin"
date: "4/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Import libraries and load data.

```{r results = "hide", warning = FALSE, message = FALSE} 
library(brglm)
library(ROSE)
```

```{r}
data <- read.csv("train.csv")

nrow(data)
data[data == -1] <- NA
data <- na.omit(data)

nrow(data)
```

Split data into train and test sets.

```{r}
train.index <- sample(nrow(data), size = nrow(data)*.8)

train.data <- data[train.index, ]
test.data <- data[-train.index, ]
```

Fit a logistic regression model using the train data, and make probabilistic predictions.

```{r warning = FALSE}
log.fit <- glm(target ~ . -id, data = train.data, family = binomial)

log.pred <- predict(log.fit, newdata = test.data, type = c("response"))
log.pred <- as.numeric(log.pred)

mean(train.data$target)
mean(log.pred)
mean((log.pred - test.data$target)^2)
hist(log.pred, breaks = 50)
max(log.pred)
```

Create binary predictions and display confusion matrix.
```{r}
threshold <- (max(log.pred) - min(log.pred))/2

log.pred.predictions <- rep(1, length(log.pred))
log.pred.predictions[log.pred <= threshold] <- 0

(confusion <- table(log.pred.predictions, test.data$target))
(specificity <- confusion[4]/(confusion[3] + confusion[4]))
(sensitivity <- confusion[1]/(confusion[1] + confusion[2]))
(error <- (confusion[2] + confusion[3])/sum(confusion))
```

Try oversampling
```{r}
oversample <- ovun.sample(target ~ ., data = train.data, method = "over")

over.fit <- glm(target ~ . -id, data = oversample$data, family = binomial)

over.pred <- predict(over.fit, newdata = test.data, type = c("response"))
hist(over.pred, breaks = 50)
mean((over.pred - test.data$target)^2)

over.pred.predictions <- rep(1, length(over.pred))
over.pred.predictions[over.pred <= 0.5] <- 0

(confusion <- table(over.pred.predictions, test.data$target))
(specificity <- confusion[4]/(confusion[3] + confusion[4]))
(sensitivity <- confusion[1]/(confusion[1] + confusion[2]))
(error <- (confusion[2] + confusion[3])/sum(confusion))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
